Diagnostics

### 2020-07-09 output_scripts/Diagnostics.Rmd
small changes to the diagnostics

---
title: "Diagnostics Week of June 28th"
author: "Owen Ward"
date: "6/30/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

@@

  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank)

@@

for(current_cohort in 1:10) {
  cat("Cohort, ", current_cohort,"\n",sep="")
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

@@

  ranks <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank)
  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)

  degs <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank,
                 out_deg = out_degree,
                 in_deg = in_degree)

>>>>

---
title: "Diagnostics"
author: "Owen Ward"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

@@

  ranks <- tibble(expert = 1:12,#expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank[expert_rank_10[[current_cohort]]])

@@

for(current_cohort in 1:10) {
  cat("Cohort ", current_cohort,"\n",sep="")
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

@@

  out_degree <- apply(sim_cohort_mmhp$gamma,2,mean)
  in_degree <- apply(sim_cohort_mmhp$zeta,2,mean)

  degs <- tibble(expert = expert_rank_10[[current_cohort]],
                  latent = mean_latent_rank,#[expert],
                 out_deg = out_degree,#[expert],
                 in_deg = in_degree)#[expert])
